Highlighting Disputed Claims on the Web

### 2010-02-09 papers/www_disputefinder/disputefinder_final.tex
Improved description of entailment algorithm and added timing figures

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/highlight_abortion.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/popup_abortion_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

There are also several tools that find pages write about the same topic with different slants, rather than looking at the specific claims a page makes. News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. 
Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

@@

These challenges are not unique to dispute finder; indeed they apply to any tool that informs a user about disputed information and helps users interpret this disputed information.

@@

Detecting entailment between texts is a semantic analysis problem. Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

@@

When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}). We also implemented and tested an interface that contained a user-editable argumentation graph; however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
	\caption{Article List interface for a disputed claim}
	\label{article_list}
	\end{center}
\end{figure}

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting ``use as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

\section{Evaluation}
\label{sec:interviews}
\label{user-studies}

@@

We also conducted interviews with most of our user study participants, and five additional people, asking them how they use the web to form and promote their opinions.

@@

When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was phrased negatively. For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.

>>>>

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/highlight_vaccine_shadow.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/popup_vaccine_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

There are also several tools that find pages written about the same topic with different slants, rather than looking at the specific claims a page makes. News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. 
Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

@@

These challenges are not unique to Dispute Finder; indeed they apply to any tool that informs a user about disputed information and helps users interpret this disputed information.

@@

Detecting entailment between texts is a semantic analysis problem. Our client side entailment method uses a simple Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006}, similar to those that are often used as a baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, applies a regular expression stemmer, and then looks for sentences that contain all the non stop-words contained in one of the paraphrases of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence.

To improve performance, rather than running the LLM algorithm for every pair of sentences and paraphrases, we compare each sentence with every paraphrase simultaneously by searching for words in order of their rareness. For each paraphrase, we sort the words in order of their rareness in Wikipedia, and then assemble a set that contains the rarerst word in every known paraphrase. If a sentence contains one of these rare words, we create a (memoized) set that contains the second-rarest word that appears in each of the paraphrases that contained the first word and then check whether the sentence contains any of these words. We repeat this process until we find a claim paraphrase such that all the non stop-words in the paraphrase are contained in the sentence.

The combination of a simple algorithm and a optimized implementation allows us to check for textual entailment between every sentence on every page a user browses and every claim paraphrase in our database with only moderate slowdown. On a 2.33Ghz Core2 processor, Dispute Finder is able to check for disputed claims on the New York Times front page in 50 milliseconds, and is able to check the Wikipedia page on Global Warming in 127 milliseconds. Moreover, to further hide this latency from users, Dispute Finder checks for disputed claims asynchronously in the background rather than forcing the user to wait. Note however that these figures are for a database with only 2,609 disputed claims. It remains to be seen how our algorithm will scale to a database with millions of disputed claims.

@@

When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{claimview}). We also implemented and tested an interface that contained a user-editable argumentation graph; however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

@@

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{claimview}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting ``use as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

\section{User Studies}
\label{sec:interviews}
\label{user-studies}

@@

We also conducted interviews with most of our user study participants, and six additional people, asking them how they use the web to form and promote their opinions.

@@

When using the article list interface (Figure~\ref{claimview}), several users got confused about whether an article supported or opposed a claim that was phrased negatively. For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.
